### 2018-01-05 articles.Rmd
初回アップロード

---
title: "Articles"
---

### in press

- Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y. (in press). How do rumination and social problem solving intensify depression? A longitudinal study. Journal of Rational-Emotive & Cognitive-Behavior Therapy

### 2017

- Moriguchi, Y., Noda, T., Nakayashiki, K., Takata, Y., Setoyama, S., Kawasaki, S., Kunisato, Y., Mishima, K., Nakagome, K., Hanakawa, T. (2017). Validation of brain-derived signals in near-infrared spectroscopy through multivoxel analysis of concurrent functional magnetic resonance imaging. Human Brain Mapping, 38(10), 5274–5291.

- Yoshimura, S., Okamoto, Y., Matsunaga, M., Onoda, K., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S. (2017). Cognitive behavioral therapy changes functional connectivity between medial prefrontal and anterior cingulate cortices, Journal of Affective Disorders, 15(208), 610-614.

### 2016

- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, A. T., & Yamawaki. (2016). Behavioral activation for late adolescents with subthreshold depression: a randomized controlled trial. European Child & Adolescent Psychiatry, 25(11), 1171-1182.

- Hasegawa, A., Nishimura, H., Matsuda, Y., Kunisato, Y., Morimoto, H., & Adachi, M. (2016). Is trait rumination associated with the ability to generate effective problem solving strategies? Utilizing two versions of the Means-Ends Problem-Solving Test. Journal of Rational-Emotive & Cognitive-Behavior Therapy, 34, 14-30.

### 2015

- Tsukue, R., Okamoto, Y., Yoshino, A., Kunisato, Y., Takagaki, K., Takebayashi, Y., Tanaka, K., Konuma, K., Tsukue, I., & Yamawaki, S. (2015) Do Individuals with Alcohol Dependence Show Higher Unfairness Sensitivity? The Relationship Between Impulsivity and Unfairness Sensitivity in Alcohol-Dependent Adults. Alcoholism, clinical and experimental research, 39(10), 2016-2021.

- Nishiyama,Y., Okamoto, Y., Kunisato, Y., Okada, G., Yoshimura, S., Kanai, Y., Yamamura, T., Yoshino, A., Jinnin, R., Takagaki, K., Onoda, K., & Yamawaki, S. (2015) fMRI Study of Social Anxiety during Social Ostracism with and without Emotional Support. PLoS ONE 10(5): e0127426.

### 2014

- Machino, A., Kunisato, Y., Matsumoto, T., Yoshimura, S., Ueda, K., Yamawaki, Y., Okada, G., Okamoto, Y., & Yamawaki, S (2014) Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, Journal of Affective Disorders, 168, 229-235.

- Yoshino, A., Okamoto, Y., Kunisato, Y., Yoshimura, Y., Jinnin, R., Hayashi, Y., Kobayakawa, M., Doi, M., Oshita, K., Nakamura, R., Tanaka, K., Yamashita, H., Kawamoto, M., & Yamawaki, S. (2014). Distinctive spontaneous regional neural activity in patients with somatoform pain disorder: A resting-state fMRI preliminary study, Psychiatry Research: Neuroimaging, 221(3), 246-248.

- Toki, S., Okamoto, Y., Onoda, K., Matsumoto, T., Yoshimura, S., Kunisato, Y., Okada, G., Shishida, K., Kobayakawa, M., Fukumoto, T., Machino, A., Inagaki, M., Yamawaki, S. (2014). Hippocampal activation during associative encoding of word pairs and its relation to symptomatic improvement in depression: A functional and volumetric MRI study. Journal of Affective Disorder, 152, 462-467.

### 2013

- Yoshimura, S., Okamoto, Y., Onoda, K., Matsunaga, M., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S. (2013). Cognitive behavioral therapy for depression changes medial prefrontal and ventral anterior cingulate cortex activity associated with self-referential processing. Social Cognitive and Affective Neuroscience, 9(4), 487-493.

- Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., Kanai, Y., Ishikawa, S., & Sakano, Y. (2013). Preliminary assessment of the behavioral activation model in Japanese undergraduate students. Psychological Reports, 112(1), 47-59.

- Koseki, S., Noda., T., Yokoyama, S., Kunisato, Y., Ito, D., Suyama, H., Matsuda, T., Sugimura, Y., Ishihara, N., Shimizu, Y., Nakazawa, K., Yoshida, S., Arima, K., Suzuki,S. (2013). The relationship between positive and negative automatic thought and activity in the prefrontal and temporal cortices: A multi-channel near-infrared spectroscopy (NIRS) study, Journal of Affective Disorders, 151(1), 352-359.

### 2012

- Kinoshita, A., Okamoto, Y., Okada, G., Demoto, Y., Kunisato, Y., Yoshimura, S., Onoda,K., Kamachi, M., Yamawaki, S. (2012) Sex differences in neural activation to ambiguous facial expression in happy and sad context, Perceptual and Motor Skills, 115(2), 349-359.

- Kunisato, Y., Okamoto, Y., Ueda, K., Onoda, K., Okada, G., Yoshimura, S., Suzuki, S., Samejima, K., Yamawaki, S. (2012) Effects of depression on reward based decision making and variability of action in probabilistic learning, Journal of Behavior Therapy and Experimental Psychiatry, 43, 1088-1094.

- Yoshino, A., Okamoto, Y., Onoda, K., Shishida, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G., Toki, S., Yamashita, H., Yamawaki, S. (2012) Sadness enhances the experience of pain and affects pain-evoked cortical activities: An MEG study, The Journal of Pain,13, 628-635.

- Demoto, Y., Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Onoda, K., Munakata, A., Nomura, M., Tanaka, S. C., Schweighofer, N., Doya, K., Yamawaki, S. (2012) Neural And Personality Correlates of Individual Differences Related to the Effects of Acute Tryptophan Depletion on Future Reward Evaluation, Neuropsychobiology, 65, 55-64.

### 2011

- Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Nishiyama, Y., Yoshimura, S., Onoda, K., Toki, S., Yamashita, H., & Yamawaki, S. (2011) The effect of negative and positive emotionality on associative memory: An fMRI study, PLoS ONE, 6(9),e24862.

- Onoda, K., Okamoto, Y., Kunisato, Y., Aoyama, S., Shishida, K., Okada, G., Tanaka, SC., Schweighofer, N., Yamaguchi, S., Doya, K., & Yamawaki, S. (2011) Inter-individual discount factor differences in reward prediction are topographically associated with caudate activation, Experimental Brain Research, 212(4), 593-601.

- Kunisato, Y., Okamoto, Y., Okada, G., Aoyama, S., Nishiyama, Y., Onoda, K., Yamawaki, S. (2011)Personality traits and the amplitude of spontaneous low-frequency oscillations during resting state, Neuroscience Letters, 492(2), 109-113.

- Kunisato,Y., Okamoto, Y., Okada, G., Aoyama, S., Demoto, Y., Munakata, A., Nomura, M., Onoda, K., Yamawaki, S. (2011) Modulation of default - mode network activity by acute tryptophan depletion is associated with mood change：A resting state functional magnetic resonance imaging study. Neuroscience Research, 69, 129-134.

### 2010

- Matsunaga, M., Okamoto, Y., Suzuki, S., Kinoshita, A., Yoshimura, S., Yoshino, A., Kunisato, Y. & Yamawaki, S. (2010). Psychosocial functioning in patients with treatment-resistant depression after group cognitive behavioral therapy. Bmc Psychiatry, 10(1), 22.

- Yoshino, A., Okamoto, Y., Onoda, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G, & Shigeto, Y. (2010). Sadness enhances the experience of pain via neural activation in the anterior cingulate cortex and amygdala: An fMRI study. Neuroimage, 50(3), 1194-1201.

### 2018-01-05 presentation.Rmd
初回アップロード

---
title: "Presentations"
---

### 2017

- Sakamoto, J., Nagai, T., Kunisato, Y., Sawa, K., Takata, N.(2017).  Bayesian modeling of human activity data based on the gamma family of dynamic models. Presented at the 50th Annual Meeting of the Society for Mathematical Psychology, July 23, Warwick, Coventry, UK.

- Somatori, K., Kunisato, Y(2017). Do depressive symptoms influence randomness in decision making in the reversal learning task? – A hierarchical Bayesian modeling approach - The 50th Annual Meeting of the Society for Mathematical Psychology, July 23, Coventry, England.

### 2016

- Sakamoto, J., Somatori, K., & Kunisato, Y. (2016). Healthy university sutudents' day-to-day pain variability , depression, and pain-catastrophising: using the experience sampling method and Bayesian linear model. Poster session presented at the 46th annual Congress of the European Association for Behavioural and Cognitive Therapies, September 1, Stockholm, Sweden.

- Somatori, K., Shimotomai, A., & Kunisato, Y. (2016). Does the Propositional Approach Co-exist Rescorla-Wagner model: the prediction of extinction form acquisition. The 46th annual Congress of the European Association for Behavioural and Cognitive Therapies, September 1, Stockholm, Sweden.

- Sakamoto, J., Okubo, M., & Kunisato, Y. (2016). How depression affects future pain and decision-making: Computational approach with Bayesiancognitive modeling. Poster session presented at the 8th World Congress of Behavioural and Cognitive Therapies, June 25, Merboulne, VIC, Australia.

- Hasegawa, A., & Kunisato, Y., Morimoto, H., Nishimura, H., Matsuda, Y. (2016) How do depression, rumination and social problem solving interact with each other? A three-wave longitudinal study. Poster session presented at the 31st International Congress of Psychology, July 26, Yokohama, Japan.

- Tsuchiya, M. & Kunisato, Y. (2016). Developing a new emotional-switching Stroop task. Poster session presented at the 31st International Congress of Psychology, July 25, Yokohama, Japan.

- Somatori, K., Shimotomai, A., & Kunisato, Y. (2016). How people estimate their confidence: Bayesian model comparison leads to a more efficient model. Poster session presented at the 31st International Congress of Psychology, July 27, Yokohama, Japan.

- Sakamoto, J., Okubo, M., & Kunisato, Y. (2016). Depression and future pain estimation: Investigating judgment process using Bayesian cognitive models. Poster session presented at the 31st International Congress of Psychology, July 27, Yokohama, Japan.

- Kaneko, M. & Kunisato, Y. (2016). Developing a behavioral task to measure procrastination using the delay-discounting paradigm. Poster session presented at the 31st International Congress of Psychology, July 28, Yokohama, Japan.

- Sakamoto, J., Somatori, K., & Kunisato, Y. (2016). Bayesian liner model for partial missing experience sampling method data: pain variability in healthy university students. Poster session presented at the 31st International Congress of Psychology, July 29, Yokohama, Japan.

### 2015

- Sakamoto, J., Somatori, K., Okubo, M., & Kunisato, Y. (2015). Depression and Intertemporal Choice of Pain: Maximum Likelihood Estimation vs. Hierarchical Bayesian Analysis. The 48th Annual Meeting of the Society for Mathematical Psychology, July 18, Newport Beach, California, USA.

- Somatori, K., Sakamoto, J., Shimotomai, A., & Kunisato, Y(2015). What is a true measure for meta-cognition?: A Bayesian cognitive modeling approach. The 48th Annual Meeting of the Society for Mathematical Psychology, July 18, Newport Beach, California, USA.

- Tanaka, T., Kunisato, Y., Okada, K., & Okubo, M. (2015). Why people frequently commit the base-rate fallacy. The 48th Annual Meeting of the Society for Mathematical Psychology, July 18, Newport Beach, California, USA.

### 2014

- Kunisato, Y., Okamoto Y., Yoshimura S., Ueda K., Matsunaga M., Okada G., Nishiyama Y., Katsuragawa T., Suzuki S., Yamawaki S. (2014) The Volume of Right Superior Temporal Gyrus Mediated the Affect of Rumination to Treatment Response to CBT in Patients with Depression The European Association for Behavioural and Cognitive Therapies, September 10 - 13 , Hague, Netherlands.

- Suzuki, S., Son, S., Yada, S., Shimizu, K., Kunisato, Y., Suyama, H., Ogawa, Y., Takei, Y., Sasaki, M., Ito, D., Koseki, S., Koseki, M., & Shirai, M. 2014 Cognitive and behavioral determinats of sick-leave duration and relapses in patients with depression. 28th International Congress of Applied Psychology, July 8-13, Paris, French(EP-060067)

- Ogawa, Y., Koga, H., Takei, Y., Shimada, M., Nagao, A., Sasaki, M., Kunisato, Y., Suyama, H., Ito, D., Koseki, M., Koseki, S., Tanigawa, K., & Suzuki,S. 2014 Communication behaviors of cancer patients who hesitate when talking to their doctors. 28th International Congress of Applied Psychology, July 8-13, Paris, French(EP-080029)

### 2013

- Ogawa, Y., Takei, Y., Koga, H., Shimada, M., Nagao, A., Sasaki, M., Kunisato, Y., Tanigawa, K., Suzuki, S. (2013). Characteristics of Cancer Outpatients who Hesitate to Speak with their Doctors During Medical Consultations, The 4th Asian Cognitive Behavior Therapy (CBT) Conference, August 23 - 25, Tokyo, Japan.

- Ogawa, Y., Takei, Y., Koga, H., Shimada, M., Nagao, A., Sasaki, M., Kunisato, Y., Tanigawa, K., Suzuki, S. (2013). Characteristics of cancer outpatients and their hesitation types while communicating with their doctors during medical consultations, 15th World Congress of Psycho-Oncology and Psychosocial Academy, November 6, Rotterdam, Netherlands.

- Yada, S., Machida, Y., Son, S., Shimizu, K., Kunisato, Y., Kaneko, Y., Suyama, H., Shirai, M., Suzuki, S. (2013). The Relationship between Periods of Sick Leave and Automatic Thoughts among Employees with Depression, The 4th Asian Cognitive Behavior Therapy (CBT) Conference, August 23 - 25, Tokyo, Japan.

### 2012

- Kunisato,Y., Okamoto, Y., Okada, G., Nishiyama, Y., Kanai, Y., Sasaki-Aoki, S., Iwanaga, M., Yamawaki, S. (2012). DELAY DISCOUNTING CORRELATED WITH ACC AND PFC: A VBM STUDY, The 16th Congress of International Society for Biomedical Research on Alcoholism (ISBRA), September 10-11, Sapporo, Japan. (Abstbook of The 16th Congress of ISBRA, P99, 2012).

- Takebayashi, Y., Tanaka, K., Tukue, R., Okamoto, Y., Kunisato, Y., Okada, G., Tsukue, I., Shimohara, C., Konuma, K., Sugiura, Y., Yamawaki, S. (2012). IMPAIRMENTS OF ATTENTIONAL FUNCTION RELATES TO DEPRESSIVE SYMPTOM DURING ABSTINENCE IN PATIENTS WITH ALCOHOL DEPENDENCE, The 16th Congress of International Society for Biomedical Research on Alcoholism (ISBRA), September 10-11, Sapporo, Japan. (Abstbook of The 16th Congress of ISBRA, P122, 2012).

- Tanaka, K., Takebayashi, Y., Tukue, R., Okamoto, Y., Kunisato, Y., Okada, G., Tsukue, I., Shimohara, C., Konuma, K., Sugiura, Y., Yamawaki, S.(2012). RELATIONSHIP BETWEEN ATTENTION CONTROL AND EMOTION DYSREGULATION IN ALCOHOL DEPENDENT PATIENTS, The 16th Congress of International Society for Biomedical Research on Alcoholism (ISBRA), September 10-11, Sapporo, Japan. (Abstbook of The 16th Congress of ISBRA, P122, 2012).

- Tsukue, R., Okamoto, Y., Kunisato, Y., Takebayashi, Y., Tanaka, K., Tsukue, I., Shimohara, C., Konuma, K., Okada, G., Sugiura, Y., Yamawaki, S. (2012). RELATIONSHIP BETWEEN DELAY DISCOUNTING, ATTENTION CONTROL AND EMOTIONAL REGULATION IN ALCOHOLISM, The 16th Congress of International Society for Biomedical Research on Alcoholism (ISBRA), September 10-11, Sapporo, Japan. (Abstbook of The 16th Congress of ISBRA, P122, 2012).

- Suzuki, S., Tanoue, A., Shimizu, K., Ohno, M., Ito, D., Suyama, H., Yokoyama, S., Kunisato, K., Okayama, N., & Son, S. (2012). Effect of Reinforcement Sensitivity on Job Satisfaction and Stress Responses,The 12th International Congress of Behavioral Medicine (ICBM), August 31, Budapest, Hungary.(International Journal of Behavioral Medicine, 19 (Suppl 1), s69-s70, 2012)

- Kunisato, Y., Okamoto, Y., Okada, G., Nishiyama, Y., Kanai, Y., Sasaki- Aoki, S., Yoshimura, S., Katsuragawa, T., Suzuki, S., & Yamawaki, S.(2012).The Association between Brain’s Default Mode Network and Anhedonia: a Resting State FMRI Study, The 12th International Congress of Behavioral Medicine (ICBM), August 29, Budapest, Hungary.(International Journal of Behavioral Medicine, 19 (Suppl 1), s258, 2012)

### 2011

- Toki, S., Okamoto, Y., Onoda, K., Yoshimura, S., Kunisato, Y., Okada, G., Yamawaki, S. (2011). Hippocampal Activation predicts Treatment Response to Antidepressant for Depression, The 50 th annual meeting of American College of Neuropsychopharmacology (ACNP), December 7, Hawaii, USA. (Abstbook of The 50 th annual meeting of American College of Neuropsychopharmacology, p324, 2011).

- Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., & Sakano, Y. (2011). Relationship between avoidant behaviors and activation on depressive symptom. Open Paper session presented at the 3rd Asian Cognitive Behavior Therapy Conference, July 14, Seoul, Korea.(Abstbook of 3rd Asian Cognitive Behavioral Therapy Conference: Searching for Asian CBT Model of Therapy and Practice, p57, 2011.) [Oral presentation]

- Yokoyama,S., Noda, T., Koseki, S., Ito, D., Kunisato, Y., Suyama, H., Sugimura, Y., Ishihara, N., Shimizu, Y., Nakazawa, K., & Suzuki, S. (2011). The relationship between frontal and temporal activation and automatic thoughts: Multi-channel near-infared spectroscopy (NIRS) study. the 3rd Asian Cognitive Behavior Therapy Conference, July 14, Seoul, Korea.(Abstbook of 3rd Asian Cognitive Behavioral Therapy Conference: Searching for Asian CBT Model of Therapy and Practice, p78, 2011.) Best Poster Award

- Kunisato, Y., Okamoto, Y., Yoshimura, S., Ueda, K., Matsunaga, M., Okada, G., Onoda, K., Suzuki, S., & Yamawaki, S. (2011). The volume of right superior temporal gyrus predicts treatment response in treatment-resistant depression patients after cognitive behavioral group therapy. the 3rd Asian Cognitive Behavior Therapy Conference, July 15, Seoul, Korea.(Abstbook of 3rd Asian Cognitive Behavioral Therapy Conference: Searching for Asian CBT Model of Therapy and Practice, p95, 2011.)

- Okayama, N., Saito, S., Ito, R., Shimizu, K., Tanoue, A., Ohono, M., Kunisato, Y., & Suzuki, S. (2011). The relations among the BIS/BAS scale for workplaces, job stressor, and stress response. the 3rd Asian Cognitive Behavior Therapy Conference, July 15, Seoul, Korea.(Abstbook of 3rd Asian Cognitive Behavioral Therapy Conference: Searching for Asian CBT Model of Therapy and Practice, p96, 2011.)

- Son, S., Ishihara, N., Suyama, H., Tanoue, A., Shimizu, K., Kunisato, Y., & Suzuki, S.(2011). The relations between cognitive coping strategies for work-stress, and positive-negative stress response. the 3rd Asian Cognitive Behavior Therapy Conference, July 15, Seoul, Korea.(Abstbook of 3rd Asian Cognitive Behavioral Therapy Conference: Searching for Asian CBT Model of Therapy and Practice, p95, 2011.)

### 2010

- Demoto, Y., Okamoto, Y., Okada, G., Kunisato, Y., Aoyama, S., Onoda, K., Munakata, A., Nomura, M., Yamawaki, S. (2010). The effects of acute tryptophan depletion and personality trait on future reward prediction. XXVII Congress of the CINP(Collegium Internationale Neuro-Psychopharmacologicum), Jun6-Jun10, Hong Kong, China. (Abstruct in The International Journal of Neuropsychopharmacology,13, p145-146, 2010.)

- Kunisato, Y., Okamoto, Y., Aoyama, S., Demoto, Y., Okada, G., Onoda, K., Munakata, A., Nomura, M., Yamawaki, S.(2010). The changes of mood are correlated to fALFF after acute tryptophan depletion : A resting fMRI study. XXVII Congress of the CINP(Collegium Internationale Neuro-Psychopharmacologicum), Jun6-Jun10, Hong Kong, China. (Abstruct in The International Journal of Neuropsychopharmacology,13, p153, 2010.)

- Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., Akita, K., Kanai, Y., Ishikawa, S., Sakano, Y. (2010). Development and validation of the Japanese version of Cognitive-Behavioral Avoidance Scale (CBAS) : From the Cross-cultural perspectives. 6th World Congress of behavioral and cognitive therapies, Jun2 - Jun 5, Boston, USA. (Abstbook of 6th WORLD CONGRESS OF BEHAVIORAL AND COGNITIVE THERAPIES Translating Science into Practice ,p113)

- Kunisato, Y., Takagaki, K., Okajima, I., Nakajima, S., Ishikawa, S., Kanai, Y., Sakano, Y., Okamoto, Y., Yamawaki, S. (2010). Development and validity of the Japanese version of Environmental Reward Observation Scale (EROS). 6th World Congress of behavioral and cognitive therapies, Jun2 - Jun 5, Boston, USA. (Abstbook of 6th WORLD CONGRESS OF BEHAVIORAL AND COGNITIVE THERAPIES Translating Science into Practice ,p114)

### 2009

- Onoda, K., Okamoto, Y., Kunisato, Y., Okada, G., Yamaguchi, S., & Yamawaki, S. (2009). High/low discounting rates in reward prediction are differentially involved in dorsal/ventral striatum. 18th The International Society for Brain Electromagnetic Topography (ISBET2009), September 29 -October 2, Kyoto, Japan.(Abstruct in the abstbook of 18th The International Society for Brain Electromagnetic Topography, p63)

### 2008

- Kunisato, Y., Ueda, K., & Suzuki, S. (2008). Relation between the depression and the sensitivity to reward and punishment. 10th International Congress of Behavioral Medicine, August 27-30, Tokyo, Japan.(Abstbook of 10th International Congress of Behavioral Medicine,p199)

### 2018-01-05 yoshihiko-kunisato.Rmd
初回アップロード

---
title: "YOSHIHIKO KUNISATO, Ph.D."
---

<img src="yoshihiko_kunisato.jpg" width="320px">

#### 学位：博士(医学)
#### 専修大学　人間科学部　心理学科　准教授
#### 1983年11月11日生まれ，兵庫県出身

#### [メールフォーム](https://docs.google.com/forms/d/1OQ7pN-oQda1YwGvcTBga3oKkviI697uc9AQlGVhX2YI/viewform)

#### [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)

#### [Researchgate](https://www.researchgate.net/profile/Yoshihiko_Kunisato)

# 学歴
#### 1999(平成11)年4月　　　兵庫県立八鹿高等学校　入学
#### 2002(平成14)年3月　　　同上　卒業
#### 2002(平成14)年4月1日 　群馬大学教育学部教育心理学専攻入学
#### 2006(平成18)年3月23日　同上　(山口陽弘研究室)卒業
#### 2006(平成18)年4月1日 　広島大学大学院教育学研究科心理学専攻(鈴木伸一研究室)　入学
#### 2008(平成20)年3月23日　同上　(大塚泰正研究室)　修了
#### 2008(平成20)年4月1日　　広島大学大学院医歯薬学総合研究科創生医科学専攻先進医療開発科学講座精神神経医科学教室(山脇成人研究室)　入学 
#### 2011(平成23)年3月23日　同上　修了

# 学位
#### 2006(平成18)年　学士（教育学）　群馬大学（第3947号)
#### 2008(平成20)年　修士（心理学）　広島大学（第25520号）「報酬・罰に対する感受性と抑うつとの関連」
#### 2011(平成23)年　博士（医学）　　広島大学（第5540号）　「Modulation of default-mode network activity by acute tryptophan depletion is associated with mood change: a resting state functional magnetic resonance imaging study」

# 職歴・教育歴
#### 2008(平成20)年7月～2009(平成21)年3月　医療法人社団更正会　草津病院　非常勤心理士
#### 2009(平成21)年4月～2011(平成23)年3月　日本学術振興会　特別研究員(DC1)
#### 2011(平成23)年4月〜2013(平成25)年3月　早稲田大学人間科学学術院　助手(鈴木伸一研究室) 
#### 2013(平成25)年4月〜2015(平成27)年3月　専修大学人間科学部心理学科　講師
#### 2011(平成23)年5月〜2016(平成28)年3月　独立行政法人　国立精神・神経医療研究センター　技術研究生
#### 2013(平成25)年5月〜　早稲田大学重点領域研究機構応用脳科学研究所　招聘研究員
#### 2015(平成27)年4月〜　専修大学人間科学部心理学科　准教授

# 非常勤講師(TA)
### 現在担当中の講義
#### 2013(平成25)年〜　早稲田大学人間科学部　非常勤講師（講義：「学習心理学」）
#### 2013(平成25)年〜　早稲田大学大学院人間科学研究科　非常勤講師（講義：「学習心理学特論」）
#### 2017(平成29年)　　早稲田大学大学院人間科学研究科　非常勤講師（講義：「臨床心理面接法特論II」）
#### 2017(平成29年)　　早稲田大学大学院人間科学研究科　非常勤講師（講義：「医療心理学・職場メンタルヘルス学ゼミ(1)A, (1)B, (2)A, (2)B」）
#### 2014(平成26)年〜　順天堂大学医学部　非常勤講師（講義：「健康の行動科学」の「行動とは何か」担当）
#### 2015(平成27)年〜　北里大学大学院看護学研究科　非常勤講師（講義：「看護研究論演習」）

### 過去に担当した講義
#### 2008(平成20)年　広島大学医学部　ティーチング・アシスタント　（講義：精神科学）
#### 2010(平成22)年　早稲田大学人間科学部通信教育課程　教育コーチ (講義： 産業カウンセリング) 
#### 2012(平成24)年　東京都立北多摩看護専門学校　非常勤講師（講義：心理学）
#### 2011(平成23)年〜2012(平成24)年　聖徳大学心理福祉学部心理学科　非常勤講師（講義：神経心理学）
#### 2013(平成25)年　お茶の水女子大学　非常勤講師　（講義：大脳生理学（と心理・行動））
#### 2014(平成26)年　聖徳大学心理福祉学部心理学科　非常勤講師（講義：神経心理学）
#### 2014(平成26)年・2016(平成28)年　東京大学教養学部統合自然科学科　非常勤講師（講義：認知行動障害論）
#### 2014(平成26)年〜2016(平成28)年　早稲田大学大学院人間科学研究科　非常勤講師（講義：「臨床心理学研究の最前線」の「医療臨床心理学研究の最前線」担当）
#### 2016(平成28)年　早稲田大学大学院文学研究科　非常勤講師（講義：「心理学特論2」）

# 研究キーワード
#### 計算論的臨床心理学，計算論的精神医学，脳機能画像研究，認知行動療法，気分・不安障害，意思決定，恐怖条件づけ

# 外部資金
#### 2009年-2010年度
#### 日本学術振興会　特別研究員研究奨励費　研究代表者
#### 「うつ病の報酬・罰に対する感受性と治療効果に関する認知神経科学的検討」

#### 2011年-2012年度
#### 日本学術振興会　研究スタート支援　研究代表者
#### 「うつ病の将来予測障害に関わる神経メカニズムの研究」

#### 2013年-2015年度
#### 日本学術振興会　若手研究(B)　研究代表者
#### 「気分障害患者の認知的情動制御不全にかかわる認知神経メカニズムの検討」

#### 2013年度
#### 日本学術振興会　基盤研究(B)　研究分担者
#### 「温熱的快適性の形成メカニズムの解析と衣服内環境評価への応用」

#### 2015年-2019年度
#### 日本学術振興会　若手研究(A)　研究代表者
#### 「恐怖条件づけの獲得・消去・再発の個人差に関わる認知機能と神経基盤」

# 学会委員
#### 日本認知・行動療法学会 2013-2018 編集委員会 編集委員
#### 日本認知・行動療法学会 2016-2018 企画委員会　委員

# 資格・免許
#### 普通自動車一種運転免許 小学校教諭免許（１種）
#### 中学校教諭免許（2種・国語）
#### 臨床心理士 心理学検定1級

# 所属学会
#### 日本心理学会　(2006年2月〜)
#### 日本認知・行動療法学会　（2006年6月〜）
#### 日本ストレス学会　（2008年3月〜）
#### 日本不安障害学会　（2009年1月〜）
#### 日本うつ病学会　（2009年1月〜）

### 2018-01-05 index.Rmd
index.htmlの更新

---
title: "Computational Clinical Psychology Lab"
---

<img src="mark.png" width="600px">

<br />

### Welcome to Computational Clinical Psychology Lab
計算論的臨床心理学研究室では，気分・不安障害のメカニズムに関する基礎研究，実証に基づく臨床心理実践のための研究，認知行動療法の効果をより高めるための研究を行っています（英語サイト作成中・・・）。

<br />

### Contact
#### Yoshihiko Kunisato, Ph.D.
#### Department of Psychology, Senshu University
#### 2-1-1, Higashimita, Tama-ku, Kawasaki-shi, 
#### Kanagawa 214-8580, Japan
#### [Mail form](https://docs.google.com/forms/d/e/1FAIpQLSeVb0_ti9flHyGcRQcLESQO7Tzl3eH5hbCqXyzcGh7RWLQexA/viewform)

### 2018-01-05 team.Rmd
index.htmlの更新

---
title: "Lab Menmbers"
---

### 教員

- [Yoshihiko Kunisato](yoshihiko-kunisato.html)

### PD

- 森 正樹　(日本学術振興会 特別研究員PD)

### 大学院生（博士2年）

- [坂本次郎](https://mrunadon.github.io/blogdown_page/post/profile/)　(日本学術振興会 特別研究員DC1)
- [杣取恵太](https://ksomatori.github.io/homepage/index.html)　(日本学術振興会 特別研究員DC1)

### 大学院生（修士２年）

- 金子美帆
- 菊池羽音
- 土谷美月

### 大学院生（修士１年）

- 井口聖香
- 土原浩平

### 学部生（４年）

- 阿久津裕史
- 福地友輔
- 関 海真
- 中川卓知
- 中西由紀奈
- 長尾雅春
- 関谷朋志

### 学部生（３年）
- 広瀬友彩 
- 小嶋那奈 
- アン ミョンヒ 
- 井上圭右 
- 小澤千尋 
- 西田千夏

### 2018-01-05 index.Rmd
英語サイトの作成

@@
 
-### Welcome to Computational Clinical Psychology Lab
-計算論的臨床心理学研究室では，気分・不安障害のメカニズムに関する基礎研究，実証に基づく臨床心理実践のための研究，認知行動療法の効果をより高めるための研究を行っています（英語サイト作成中・・・）。
+### Welcome 
+Welcome to the Computational Clinical Psychology Lab.
+Our research interests are (1)  impairments of decision making in depression using the bayesian cognitive modelling, (2) fear conditioning in anxiety disorders using the neural network model, (3) evedence based practce in clinical psychology.The Computational Clinical Psychology Lab is directed by Yoshihiko Kunisato, Ph.D.
 
@@
 #### Department of Psychology, Senshu University
-#### 2-1-1, Higashimita, Tama-ku, Kawasaki-shi, 
-#### Kanagawa 214-8580, Japan
-#### [Mail form](https://docs.google.com/forms/d/e/1FAIpQLSeVb0_ti9flHyGcRQcLESQO7Tzl3eH5hbCqXyzcGh7RWLQexA/viewform)
+#### ADRESS: 2-1-1, Higashimita, Tama-ku, Kawasaki-shi, Kanagawa 214-8580, Japan
+#### E-MAIL: ykunisato<at>psy.senshu-u.ac.jp

### 2018-01-05 team.Rmd
英語サイトの作成

@@
 ---
-title: "Lab Menmbers"
+title: "Team"
 ---
 
-### 教員
+### Principal investigator
 
@@
 
-### PD
+### Postdoctoral Fellow
 
-- 森 正樹　(日本学術振興会 特別研究員PD)
+- Masaki Mori　(JSPS Research Fellowship for Young Scientists, Postdoctoral Fellow (PD))
 
-### 大学院生（博士2年）
+### Ph.D. students
 
-- [坂本次郎](https://mrunadon.github.io/blogdown_page/post/profile/)　(日本学術振興会 特別研究員DC1)
-- [杣取恵太](https://ksomatori.github.io/homepage/index.html)　(日本学術振興会 特別研究員DC1)
+- [Jiro Sakamoto](https://mrunadon.github.io/blogdown_page/post/profile/)　(JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1))
+- [Keita Somatori](https://ksomatori.github.io/homepage/index.html)　(JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1))
 
-### 大学院生（修士２年）
+### Master Course students
 
-- 金子美帆
-- 菊池羽音
-- 土谷美月
+- Miho Kaneko
+- Wato Kikuchi
+- Mizuki Tsuchiya
+- Seika Iguchi
+- Kohei Tsuchihara
 
-### 大学院生（修士１年）
+### Undergraduate students
 
-- 井口聖香
-- 土原浩平
-
-### 学部生（４年）
-
-- 阿久津裕史
-- 福地友輔
-- 関 海真
-- 中川卓知
-- 中西由紀奈
-- 長尾雅春
-- 関谷朋志
-
-### 学部生（３年）
-- 広瀬友彩 
-- 小嶋那奈 
-- アン ミョンヒ 
-- 井上圭右 
-- 小澤千尋 
-- 西田千夏
+- Hirofumi Akutsu
+- Yusuke Fukuchi
+- Kaima Seki
+- Takuto Nakagawa
+- Yukina Nakanishi
+- Masaharu Nagao
+- Tomoyuki Sekiya
+- Yua Hirose 
+- Nana Kojima 
+- Myeonghee Ahn 
+- keisuke Inoue 
+- Chihiro Ozawa 
+- Chika Nishida

### 2018-01-05 yoshihiko-kunisato.Rmd
英語サイトの作成

@@
 
-#### 学位：博士(医学)
-#### 専修大学　人間科学部　心理学科　准教授
-#### 1983年11月11日生まれ，兵庫県出身
-
-#### [メールフォーム](https://docs.google.com/forms/d/1OQ7pN-oQda1YwGvcTBga3oKkviI697uc9AQlGVhX2YI/viewform)
-
+## PERSONAL INFORMATION
+####  Yoshihiko Kunisato
+####  Associate Professor of Clinical Psychology
+####  Department of Psychology,School of Human Sciences, SENSHU UNIVERSITY
+####  DATE OF BIRTH: November 11, 1983
+####  PLACE OF BIRTH: Hyougo Japan
+####  CITIZENSHIP: Japanese
+####  ADRESS: 2-1-1, Higashi-Mita, Tama, Kawasaki, 214-8580, JAPAN
+####  E-MAIL: ykunisato<at>psy.senshu-u.ac.jp
 ####  [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)
-
 ####  [Researchgate](https://www.researchgate.net/profile/Yoshihiko_Kunisato)
 
-# 学歴
-#### 1999(平成11)年4月　　　兵庫県立八鹿高等学校　入学
-#### 2002(平成14)年3月　　　同上　卒業
-#### 2002(平成14)年4月1日 　群馬大学教育学部教育心理学専攻入学
-#### 2006(平成18)年3月23日　同上　(山口陽弘研究室)卒業
-#### 2006(平成18)年4月1日 　広島大学大学院教育学研究科心理学専攻(鈴木伸一研究室)　入学
-#### 2008(平成20)年3月23日　同上　(大塚泰正研究室)　修了
-#### 2008(平成20)年4月1日　　広島大学大学院医歯薬学総合研究科創生医科学専攻先進医療開発科学講座精神神経医科学教室(山脇成人研究室)　入学 
-#### 2011(平成23)年3月23日　同上　修了
+## EDUCATION
+####  2002 - 2006 Faculty of Education, Gunma University
+####  2006 - 2008 Master Course, Graduate School of Education, Hiroshima University
+####  2008 - 2011 Doctor Course, Graduate School of Biomedical Science, Hiroshima University
 
-# 学位
-#### 2006(平成18)年　学士（教育学）　群馬大学（第3947号)
-#### 2008(平成20)年　修士（心理学）　広島大学（第25520号）「報酬・罰に対する感受性と抑うつとの関連」
-#### 2011(平成23)年　博士（医学）　　広島大学（第5540号）　「Modulation of default-mode network activity by acute tryptophan depletion is associated with mood change: a resting state functional magnetic resonance imaging study」
+## PROFESSIONAL CERTIFICATION
+####  2006 Bachelor of Education, Gunma University
+####  2008 Master of Science in Clinical Psychology, Hiroshima University
+####  2011 Doctor of Philosophy in Medical Science, Hiroshima University
 
-# 職歴・教育歴
-#### 2008(平成20)年7月～2009(平成21)年3月　医療法人社団更正会　草津病院　非常勤心理士
-#### 2009(平成21)年4月～2011(平成23)年3月　日本学術振興会　特別研究員(DC1)
-#### 2011(平成23)年4月〜2013(平成25)年3月　早稲田大学人間科学学術院　助手(鈴木伸一研究室) 
-#### 2013(平成25)年4月〜2015(平成27)年3月　専修大学人間科学部心理学科　講師
-#### 2011(平成23)年5月〜2016(平成28)年3月　独立行政法人　国立精神・神経医療研究センター　技術研究生
-#### 2013(平成25)年5月〜　早稲田大学重点領域研究機構応用脳科学研究所　招聘研究員
-#### 2015(平成27)年4月〜　専修大学人間科学部心理学科　准教授
+## ACADEMIC APPOINTMENTS AND EMPLOYMENT
+####  2009 – 2011 JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1)
+####  2011 - 2013 Research Associate,Faculty of Human Sciences, Waseda University
+####  2013 -2015 Lecturer (with tenure),Faculty of Human Sciences, Senshu University
+####  2015- Associate Professor, Faculty of Human Sciences, Senshu University
 
-# 非常勤講師(TA)
-### 現在担当中の講義
-#### 2013(平成25)年〜　早稲田大学人間科学部　非常勤講師（講義：「学習心理学」）
-#### 2013(平成25)年〜　早稲田大学大学院人間科学研究科　非常勤講師（講義：「学習心理学特論」）
-#### 2017(平成29年)　　早稲田大学大学院人間科学研究科　非常勤講師（講義：「臨床心理面接法特論II」）
-#### 2017(平成29年)　　早稲田大学大学院人間科学研究科　非常勤講師（講義：「医療心理学・職場メンタルヘルス学ゼミ(1)A, (1)B, (2)A, (2)B」）
-#### 2014(平成26)年〜　順天堂大学医学部　非常勤講師（講義：「健康の行動科学」の「行動とは何か」担当）
-#### 2015(平成27)年〜　北里大学大学院看護学研究科　非常勤講師（講義：「看護研究論演習」）
-
-### 過去に担当した講義
-#### 2008(平成20)年　広島大学医学部　ティーチング・アシスタント　（講義：精神科学）
-#### 2010(平成22)年　早稲田大学人間科学部通信教育課程　教育コーチ (講義： 産業カウンセリング) 
-#### 2012(平成24)年　東京都立北多摩看護専門学校　非常勤講師（講義：心理学）
-#### 2011(平成23)年〜2012(平成24)年　聖徳大学心理福祉学部心理学科　非常勤講師（講義：神経心理学）
-#### 2013(平成25)年　お茶の水女子大学　非常勤講師　（講義：大脳生理学（と心理・行動））
-#### 2014(平成26)年　聖徳大学心理福祉学部心理学科　非常勤講師（講義：神経心理学）
-#### 2014(平成26)年・2016(平成28)年　東京大学教養学部統合自然科学科　非常勤講師（講義：認知行動障害論）
-#### 2014(平成26)年〜2016(平成28)年　早稲田大学大学院人間科学研究科　非常勤講師（講義：「臨床心理学研究の最前線」の「医療臨床心理学研究の最前線」担当）
-#### 2016(平成28)年　早稲田大学大学院文学研究科　非常勤講師（講義：「心理学特論2」）
-
-# 研究キーワード
-#### 計算論的臨床心理学，計算論的精神医学，脳機能画像研究，認知行動療法，気分・不安障害，意思決定，恐怖条件づけ
-
-# 外部資金
-#### 2009年-2010年度
-#### 日本学術振興会　特別研究員研究奨励費　研究代表者
-#### 「うつ病の報酬・罰に対する感受性と治療効果に関する認知神経科学的検討」
-
-#### 2011年-2012年度
-#### 日本学術振興会　研究スタート支援　研究代表者
-#### 「うつ病の将来予測障害に関わる神経メカニズムの研究」
-
-#### 2013年-2015年度
-#### 日本学術振興会　若手研究(B)　研究代表者
-#### 「気分障害患者の認知的情動制御不全にかかわる認知神経メカニズムの検討」
-
-#### 2013年度
-#### 日本学術振興会　基盤研究(B)　研究分担者
-#### 「温熱的快適性の形成メカニズムの解析と衣服内環境評価への応用」
-
-#### 2015年-2019年度
-#### 日本学術振興会　若手研究(A)　研究代表者
-#### 「恐怖条件づけの獲得・消去・再発の個人差に関わる認知機能と神経基盤」
-
-# 学会委員
-#### 日本認知・行動療法学会 2013-2018 編集委員会 編集委員
-#### 日本認知・行動療法学会 2016-2018 企画委員会　委員
-
-# 資格・免許
-#### 普通自動車一種運転免許 小学校教諭免許（１種）
-#### 中学校教諭免許（2種・国語）
-#### 臨床心理士 心理学検定1級
-
-# 所属学会
-#### 日本心理学会　(2006年2月〜)
-#### 日本認知・行動療法学会　（2006年6月〜）
-#### 日本ストレス学会　（2008年3月〜）
-#### 日本不安障害学会　（2009年1月〜）
-#### 日本うつ病学会　（2009年1月〜）
+## PROFESSIONAL SOCIETIES
+####  The Japanese Psychological Association (JPA) Member, 2006-present
+####  Japanese Association of Behavior Therapy (JABT) Member, 2006-present
+####  The Japanese Association of Stress Science (JASS) Member, 2008-present

### 2018-01-06 index.Rmd
メールアドレスの修正

@@
 #### ADRESS: 2-1-1, Higashimita, Tama-ku, Kawasaki-shi, Kanagawa 214-8580, Japan
-#### E-MAIL: ykunisato<at>psy.senshu-u.ac.jp
+#### E-MAIL:ykunisato (at sign) psy.senshu-u.ac.jp

### 2018-01-06 yoshihiko-kunisato.Rmd
メールアドレスの修正

@@
 ####  ADRESS: 2-1-1, Higashi-Mita, Tama, Kawasaki, 214-8580, JAPAN
-####  E-MAIL: ykunisato<at>psy.senshu-u.ac.jp
+####  E-MAIL: ykunisato (at sign) psy.senshu-u.ac.jp
 ####  [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)

### 2018-04-04 team.Rmd
チームの追加

--- 2018-01-05 team.Rmd
@@
 
-### PD
+### Postdoctoral Fellow
 
-- 森 正樹　(日本学術振興会 特別研究員PD)
+### Ph.D. students
 
-### 大学院生（博士2年）
+- [Keita Somatori](https://ksomatori.github.io/homepage/index.html)　(JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1))
 
-- [坂本次郎](https://mrunadon.github.io/blogdown_page/post/profile/)　(日本学術振興会 特別研究員DC1)
-- [杣取恵太](https://ksomatori.github.io/homepage/index.html)　(日本学術振興会 特別研究員DC1)
+### Master Course students
 
-### 大学院生（修士２年）
+- Seika Iguchi
+- Kohei Tsuchihara
+- Takuto Nakagawa
 
-- 金子美帆
-- 菊池羽音
-- 土谷美月
+### Undergraduate students
 
-### 大学院生（修士１年）
-
-- 井口聖香
-- 土原浩平
-
-### 学部生（４年）
-
-- 阿久津裕史
-- 福地友輔
-- 関 海真
-- 中川卓知
-- 中西由紀奈
-- 長尾雅春
-- 関谷朋志
-
-### 学部生（３年）
-- 広瀬友彩 
-- 小嶋那奈 
-- アン ミョンヒ 
-- 井上圭右 
-- 小澤千尋 
-- 西田千夏
+- Hirofumi Akutsu
+- Yua Hirose 
+- Nana Kojima 
+- Myeonghee Ahn 
+- keisuke Inoue 
+- Chihiro Ozawa 
+- Chika Nishida
+- Runa Kikuchi
+- Mai Shibata
+- Momoka Shibaya
+- Nodoka Inoue
+- Sakina Inoue
+- Natsumi Oofusa
+- Kaito Suzuki

### 2018-07-23 articles.Rmd
英語サイトの作成
業績更新
高垣くん論文アクセプト

@@
 ---
-title: "Articles"
+title: "Journal Articles"
 ---
@@
 
+- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T.
+A., & Yamawaki.
+(in press).
+Enduring effects of a five-week behavioral activation program for subthreshold depression among late adolescents: an exploratory randomized controlled trial.
+Neuropsychiatric Disease and Treatment .
+
 - Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
 (in press).
+Depressive rumination and urgency have mutually enhancing relationships but both predict unique variance in future depression: A longitudinal study.
+Cogent Psychology.
+
+### 2018
+
+- Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
+(2018).
 How do rumination and social problem solving intensify depression?
 A longitudinal study.
-Journal of Rational-Emotive & Cognitive-Behavior Therapy
+Journal of Rational-Emotive & Cognitive-Behavior Therapy, 36, 1, 28-46.
 

### 2019-10-15 articles.Rmd
update the publication
add in press
update

@@
 
-- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T.
-A., & Yamawaki.
-(in press).
-Enduring effects of a five-week behavioral activation program for subthreshold depression among late adolescents: an exploratory randomized controlled trial.
-Neuropsychiatric Disease and Treatment .
+- Nishiguchi, Y., Sakamoto, J., Kunisato, Y., & Takano, K.
+(in press) Linear Ballistic Accumulator Modeling of Attentional Bias Modification Revealed Disturbed Evidence Accumulation of Negative Information by Explicit Instruction.
+Frontiers in Psychology,
+
+- Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K (in press).
+Gambling symptoms, behaviors, and cognitive distortions in Japanese university students.
+Substance Abuse Treatment, Prevention, and Policy,
+
+### 2019
+
+- Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y.
+(2019).
+Associations between self-reported impulsivity and a latent variable of impulsive action constructed from three laboratory tasks.
+Journal of Experimental Psychopathology, 10, 3.
+doi: 10.1177/2043808719861894
+
+### 2018
 
 - Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
-(in press).
+(2018).
 Depressive rumination and urgency have mutually enhancing relationships but both predict unique variance in future depression: A longitudinal study.
-Cogent Psychology.
-
-### 2018
+Cogent Psychology, 5: 1450919.ß
 
@@
 Journal of Rational-Emotive & Cognitive-Behavior Therapy, 36, 1, 28-46.
+
+- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T.
+A., & Yamawaki.
+(2018).
+Enduring effects of a five-week behavioral activation program for subthreshold depression among late adolescents: an exploratory randomized controlled trial.
+Neuropsychiatric Disease and Treatment , 14, 2633-2641.
 

### 2020-07-23 articles.Rmd
update 23-07-2020

@@
 
-### in press
+### 2020
+
+- Katahira, K., Kunisato, Y., Okimura, T., & Yamashita, Y.
+(2020) Retrospective surprise: A computational component for active inference.
+Journal of Mathematical Psychology, 96, 102347.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S0022249620300286?dgcid=author)
+
+- Katahira, K., Kunisato, Y., Yamashita, Y., & Suzuki, S.
+(2020) Commentary: "A robust data-driven approach identifies four personality types across four large data sets".
+Frontiers in Big Data, 3(8).
+[Link](https://www.frontiersin.org/articles/10.3389/fdata.2020.00008/full)
+
+### 2019
 
 - Nishiguchi, Y., Sakamoto, J., Kunisato, Y., & Takano, K.
-(in press) Linear Ballistic Accumulator Modeling of Attentional Bias Modification Revealed Disturbed Evidence Accumulation of Negative Information by Explicit Instruction.
-Frontiers in Psychology,
+(2019) Linear Ballistic Accumulator Modeling of Attentional Bias Modification Revealed Disturbed Evidence Accumulation of Negative Information by Explicit Instruction.
+Frontiers in Psychology,10, 2447.
+[Link](https://www.frontiersin.org/articles/10.3389/fpsyg.2019.02447/full)
 
-- Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K (in press).
+- Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K.
+(2019).
 Gambling symptoms, behaviors, and cognitive distortions in Japanese university students.
-Substance Abuse Treatment, Prevention, and Policy,
-
-### 2019
+Substance Abuse Treatment, Prevention, and Policy, 14, 51.
+[Link](https://substanceabusepolicy.biomedcentral.com/articles/10.1186/s13011-019-0230-5)
 
@@
 Journal of Experimental Psychopathology, 10, 3.
-doi: 10.1177/2043808719861894
+[Link](https://journals.sagepub.com/doi/full/10.1177/2043808719861894)
 
@@
 Depressive rumination and urgency have mutually enhancing relationships but both predict unique variance in future depression: A longitudinal study.
-Cogent Psychology, 5: 1450919.ß
+Cogent Psychology, 5: 1450919.ß [Link](https://www.tandfonline.com/doi/full/10.1080/23311908.2018.1450919)
 
@@
 Journal of Rational-Emotive & Cognitive-Behavior Therapy, 36, 1, 28-46.
+[Link](https://link.springer.com/article/10.1007/s10942-017-0272-4)
 
@@
 Neuropsychiatric Disease and Treatment , 14, 2633-2641.
+[Link](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6186299/)
 
@@
 Human Brain Mapping, 38(10), 5274–5291.
+[Link](https://onlinelibrary.wiley.com/doi/full/10.1002/hbm.23734)
 
@@
 Cognitive behavioral therapy changes functional connectivity between medial prefrontal and anterior cingulate cortices, Journal of Affective Disorders, 15(208), 610-614.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S0165032716305195)
 
@@
 European Child & Adolescent Psychiatry, 25(11), 1171-1182.
+[Link](https://link.springer.com/article/10.1007/s00787-016-0842-5)
 
@@
 Journal of Rational-Emotive & Cognitive-Behavior Therapy, 34, 14-30.
+[Link](https://pubmed.ncbi.nlm.nih.gov/26900257/)
 
@@
 Alcoholism, clinical and experimental research, 39(10), 2016-2021.
+[Link](https://onlinelibrary.wiley.com/doi/abs/10.1111/acer.12832)
 
@@
 PLoS ONE 10(5): e0127426.
+[Link](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0127426)
 
@@
 - Machino, A., Kunisato, Y., Matsumoto, T., Yoshimura, S., Ueda, K., Yamawaki, Y., Okada, G., Okamoto, Y., & Yamawaki, S (2014) Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, Journal of Affective Disorders, 168, 229-235.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S0165032714003917?via%3Dihub)
 
@@
 Distinctive spontaneous regional neural activity in patients with somatoform pain disorder: A resting-state fMRI preliminary study, Psychiatry Research: Neuroimaging, 221(3), 246-248.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S0925492713003417?via%3Dihub)
 
@@
 Journal of Affective Disorder, 152, 462-467.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S0165032713005892?via%3Dihub)
 
@@
 Social Cognitive and Affective Neuroscience, 9(4), 487-493.
+[Link](https://academic.oup.com/scan/article/9/4/487/1629777)
 
@@
 Psychological Reports, 112(1), 47-59.
+[Link](https://journals.sagepub.com/doi/abs/10.2466/02.15.21.PR0.112.1.47-59)
 
@@
 The relationship between positive and negative automatic thought and activity in the prefrontal and temporal cortices: A multi-channel near-infrared spectroscopy (NIRS) study, Journal of Affective Disorders, 151(1), 352-359.
+[Link](https://www.sciencedirect.com/science/article/pii/S0165032713004461)
 
@@
 (2012) Sex differences in neural activation to ambiguous facial expression in happy and sad context, Perceptual and Motor Skills, 115(2), 349-359.
+[Link](https://journals.sagepub.com/doi/abs/10.2466/22.24.PMS.115.5.349-359)
 
@@
 (2012) Effects of depression on reward based decision making and variability of action in probabilistic learning, Journal of Behavior Therapy and Experimental Psychiatry, 43, 1088-1094.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S000579161200047X?via%3Dihub)
 
@@
 (2012) Sadness enhances the experience of pain and affects pain-evoked cortical activities: An MEG study, The Journal of Pain,13, 628-635.
+[Link](Sadness enhances the experience of pain and affects pain-evoked cortical activities: An MEG study)
 
@@
 (2012) Neural And Personality Correlates of Individual Differences Related to the Effects of Acute Tryptophan Depletion on Future Reward Evaluation, Neuropsychobiology, 65, 55-64.
+[Link](https://www.karger.com/Article/Abstract/328990)
 
@@
 (2011) The effect of negative and positive emotionality on associative memory: An fMRI study, PLoS ONE, 6(9),e24862.
+[Link](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0024862)
 
@@
 (2011) Inter-individual discount factor differences in reward prediction are topographically associated with caudate activation, Experimental Brain Research, 212(4), 593-601.
+[Link](https://link.springer.com/article/10.1007/s00221-011-2771-3)
 
@@
 (2011)Personality traits and the amplitude of spontaneous low-frequency oscillations during resting state, Neuroscience Letters, 492(2), 109-113.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S0304394011001133)
 
@@
 Neuroscience Research, 69, 129-134.
+[Link](https://www.sciencedirect.com/science/article/pii/S016801021002835X?via%3Dihub)
 
@@
 Bmc Psychiatry, 10(1), 22.
+[Link](https://bmcpsychiatry.biomedcentral.com/articles/10.1186/1471-244X-10-22)
 
@@
 Neuroimage, 50(3), 1194-1201.
+[Link](https://www.sciencedirect.com/science/article/abs/pii/S1053811909012658)

### 2020-07-23 presentation.Rmd
英語サイトの作成
update 23-07-2020

@@
 ---
-title: "Presentations"
+title: "Conference presentation"
 ---
+
+### 2019
+
+- Kunisato, Y.
+(2019).
+Relationship between metacognition of reversal learning and interoception, anxiety, and depression.
+The First European Congress on Clinical Psychology and Psychological Treatment of EACLIPT
+November 1, Dresden, Germany.
+
+- Kunisato, Y.
+& Sawa, K.(2019).
+Obsessive-compulsive tendency attenuates the recovery from overshadowing in associative learning.
+The 52nd Annual Meeting of the Society for Mathematical Psychology, July 20, Montreal, Canada.
+
+- Hata, K., Ono, H., Ogawa, Y., Takeshita, W., Kunisato, Y., & Suzuki, S.
+(2019).
+Development and validation of the activity restriction scale for cancer patients (Sickness Impact Profile for Cancer Patients: SIP-C).
+The 9th World Congress of Behavioural and Cognitive Therapies, July 20, Berlin, Germany.
 

### 2020-07-23 team.Rmd
update 23-07-2020

@@
 
+- [Asako Toyama](https://t-asa.github.io/homepage/index.html)
+
 ### Ph.D. students
 
-- [Keita Somatori](https://ksomatori.github.io/homepage/index.html)　(JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1))
+- [Keita Somatori](https://ksomatori.github.io/homepage/index.html)
 
@@
 
-- Seika Iguchi
-- Kohei Tsuchihara
-- Takuto Nakagawa
+- Keisuke Inoue
+- Satoshi Yamazaki
 
@@
 
-- Hirofumi Akutsu
-- Yua Hirose 
-- Nana Kojima 
-- Myeonghee Ahn 
-- keisuke Inoue 
-- Chihiro Ozawa 
-- Chika Nishida
-- Runa Kikuchi
-- Mai Shibata
-- Momoka Shibaya
-- Nodoka Inoue
-- Sakina Inoue
-- Natsumi Oofusa
-- Kaito Suzuki
+- Yukiko Saito
+- Jihee Woo
+- Ryota Tanaka
+- Daichi Igarashi
+- Naoki Sawamura
+- Shu Ensei
+- Koji Komine

### 2020-07-23 yoshihiko-kunisato.Rmd
update 23-07-2020

@@
 ####  Japanese Association of Behavior Therapy (JABT) Member, 2006-present
-####  The Japanese Association of Stress Science (JASS) Member, 2008-present

### 2021-07-24 articles.Rmd
update

@@
 
+### in press
+
+- Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y.
+(in press).
+Depression, rumination, and impulsive action: A latent variable approach to behavioral impulsivity.
+The Journal of Psychology.
+
+- Wang, K., Goldenberg, A., Dorison, C., Miller, J.
+K.
+P., Uusberg, A., Lerner, J.
+S., Gross, J., Marcu, G.
+M., Agadullina, E., Adamkovic, M., Roczniewska, M., Kassianos, A., Dursun, P., Arinze, A.
+I., Arinze, N.
+C., Ogbonnaya, C., Ndukaihe, I.
+L.
+G., Dalgar, I., Akkas, H., Macapagal, P.
+M.
+L., Lewis, S., Metin-Orta, I., Willis, M., Santos, A.
+C., Mokady, A., Reggev, N., Vasilev, M.
+R., Nock, N.
+L., Parzuchowski, M., Barría, M.
+E., Vranka, M.
+A., Ropovik, I., Yao, X., Becker, M., Manunta, E., Kaminski, G., Findor, A., Lewis, D.
+M.
+G., Aruta, J.
+J.
+B.
+R., Zickfeld, J., Vásquez, J.
+C., Pronizius, E., Lamm, C., Li, R., Valentova, J.
+V., Mioni, G., Cellini, N., Chen, S.-C., Moon, K., Azab, H., Todsen, A.
+L., van Schie, K., Bavolar, J., Warmelink, L., Ross, R.
+M., Stephen, I.
+D., Hostler, T., McCarthy, R.
+J., Grano, C., Singh Solorzano, C., Kácha, O., Arvanitis, A., Xiao, Q., Cárcamo, R., Zorjan, S., Tajchman, Z.
+J., Vilares, I., Pavlacic, J.
+M., Kunst, J.
+R., Tamnes, C.
+K., Atari, M., Sharifian, M., Hricova, M., Kačmár, P., Rahal, R.-M., Zakharov, I., Koehn, M.
+A., Esteban Serna, C., Hajdu, N., Calin-Jageman, R., Krafnick, A.
+J., Očovaj, S.
+B., Khosla, M., Urban, J., Boudesseul, J., Silva, J., Martončik, M., Šakan, D., Kuzminska, A., Djordjevic, J.
+M., Almeida, I.
+A.
+T., Lazarevic, L.
+B., Manley, H., Zambrano, D., Monteiro, R.
+P., Musser, E.
+D., Dunleavy, D.
+J., Godbersen, H., Ruiz-Fernandez, S., Reeck, C., Batres, C., Azevedo, F., Alvarez, D.
+S., Chen, Z., Verbruggen, F., Ziano, I., Tümer, M., Dubrov, D., Karababa, A., del Carmen, M., Aberson, C., Moller, A.
+C., Hubená, B., Ceary, C., Singer, G.
+A., Perillo, J.
+T., Ballantyne, T., Du, H., Pit, I.
+L., Hruška, M., Sousa, D., Aczel, B., Szaszi, B., Barzykowski, K., Micheli, L., Zsido, A.
+N., Paruzel-Czachura, M., Bialek, M., Kowal, M., Sorokowska, A., Misiak, M., Arriaga, P., Oliveira, R.
+A., Vaughn, L.
+A., Szwed, P., Kossowska, M., Kielińska, J., Antazo, B.
+G., Stieger, S., Nilsonne, G., simonovic, N., Taber, J.
+M., Gourdon-Kanhukamwe, A., Domurat, A., Ihaya, K., Yamada, Y., Urooj, A., Gill, T., Bylinina, L., Baklanova, E., Albayrak-Aydemir, N., Kappes, H.
+B., Gjoneska, B., House, T., Berkessel, J., Muda, R., Chopik, W.
+J., Çoksan, S., Seehuus, M., Khaoudi, A., Azouaghe, S., Arabi, K.
+A.
+E., Djamai, I., Wilson, J.
+P., Adiguzel, A., Kocalar, H.
+E., Norton, J., Papadatou-Pastou, M., Evans, K., Chuan-Peng, H., De la Rosa-Gomez, A., Ankushev, V., Bogatyreva, N., Grigoryev, D., Ivanov, A., Prusova, I., Romanova, M., Sarieva, I., Terskova, M., Hristova, E., Janak, A., Schei, V., Sverdrup, T.
+E., Askelund, A.
+D., Collins, W.
+M., Boucher, L., Ouherrou, N., Schrötter, J., Bokkour, A., Say, N., Sinkolova, S., Janjić, K., Stojanovska, D., Bijlstra, G., Mosannenzadeh, F., Reips, U.-D., Baskin, E., Ishkhanyan, B., Czamanski-Cohen, J., Dixson, B., Moreau, D., Sutherland, C., Noone, C., Anne, M., Janssen, S.
+M.
+J., Fu, C.
+H., Majeed, N.
+M., Kunisato, Y., Daches, S., Hartanto, A., Vdovic, M., Forbes, P., Kamburidis, J., Rachev, N.
+R., Stoyanova, A., Marinova, E., Schmidt, K., Suchow, J.
+W., Koptjevskaja-Tamm, M., Jernsäther, T., Olofsson, J., Bialobrzeska, O., Marszalek, M., Tatachari, S., Afhami, R., Law, W., Zuro, B., Van Doren, N., Soto, J., Searston, R.
+A., Miranda, J.
+F., Yeung, S.
+K., Krupić, D., Jaeger, B., Ren, D., Pfuhl, G., Klevjer, K., Vally, Z., Vargas-Nieto, J.
+C., Corral-Frías, N.
+S., Frias-Armenta, M., Lucas, M.
+Y., Torres, A.
+O., Toro, M., Vega, D., Solas, S.
+Á., Vilar, R., Massoni, S., Reyna, C., Pöntinen, S.
+J., Adetula, G.
+A., Foroni, F.
+P., Kurfali, M.
+A., Braun Kohlová, M., Harutyunyan, M., Landry, A.
+T., Ortiz, M., Voracek, M., Grinberg, M., Vintr, J., Kaliska, L., Pourafshari, R., Geiger, S.
+J., Beitner, J., Szala, A., Anjum, G., von Bastian, C.
+C., Cohen, N., Kirgizova, K., Muminov, A., Butt, M.
+M., Lee, J.
+M., Charyate, A., Sacakli, A., Richard, K., Cyrus-Lai, W., Fedotov, M., Wielgus, M., Adamus, S., Mola, D., Correa, P.
+S., Belaus, A., Muchembled, F., Ribeiro, R.
+R., Abbas, N., Čadek, M., Messerschmidt, J., Adetula, A., Kadreva, V., Bran, A., Vaidis, D.
+C., Vieira, L., Coelho, G.
+L.
+H., Whitt, C.
+M., Tullett, A.
+M., Du, X., Volz, L., Sarioguz, E., Korbmacher, M., Lima, T., Ribeiro, M.
+F.
+F., Verharen, J., Karekla, M., Jaremka, L.
+M., Storage, D., Studzinska, A., Hanel, P.
+H.
+P., Holford, D.
+L., Sirota, M., Wolfe, K., Chiu, F., Theodoropoulou, A., Ahn, E.
+R., Lin, Y., Westgate, E.
+C., Hofer, G., Vezirian, K., Travaglino, G.
+A., Marko, D., Li, M., Torunsky, N., Manavalan, M., Song, X., Walczak, R.
+B., Zdybek, P., Dalla Rosa, A., Kozma, L., Alves, S.
+G., Correia, R., Pinto, I.
+R., Babincak, P., Baník, G., Varella, M.
+A.
+C., Uttley, J., Beshears, J., Thommesen, K.
+K., Behzadnia, B., Bradford, M., Geniole, S., Silan, M.
+A., Vilsmeier, J.
+K., Tran, U.
+S., Morales-Izquierdo, S., Mensink, M.
+C., Groyecka-Bernard, A., Sorokowski, P., Radtke, T., Özdoğru, A.
+A., Ishii, T., Wichman, A.
+L., Röer, J.
+P., Ostermann, T., Davis, W.
+E., Suter, L., Ferreira, A., Agesin, B.
+B., Rana, K., Eudave, L., Campos, O., Grzech, K., Hausman Ozery, D., Jackson, E.
+A., Jimenez-Leal, W., Krizanic, V., Garcia, E.
+O.
+L., Drexler, S.
+M., Jurković, A.
+P., Štrukelj, E., Antoniadi, M., Desai, K., Gialitaki, Z., Kushnir, E., Nadif, K., Bravo, O.
+N., Nauman, R., Oosterlinck, M., Pantazi, M., Pilecka, N., Szabelska, A., van Steenkiste, I.
+M.
+M., Filip, K., Bozdoc, A.
+I., Westerlund, M., Ahlgren, L., Wang, C., Levy, N.
+L., Beaudry, J.
+L., Samojlenko, L., Isager, P.
+M., Chou, W., Pálfi, B., Schmidt, N.-D., Ortiz, M.
+V., Czarnek, G., Jones, M., Berkessel, J.
+B., Iyer, A., Parashar, N., Bundt, C., Pineda, L.
+M.
+S., Thomas, A.
+G., Kung, F.
+Y.
+H., Balci, B.
+B., Flowe, H.
+D., Topor, M., Yu, K., Anton-Boicuk, L., Kurfalı, M., Antfolk, J., Damnjanović, K., Hoyer, K., Galindo-Caballero, O.
+J., Calderón Pérez, L., Delgado, G.
+J., Frizzo, T., Capizzi, M., Greenburgh, A., Bosma, M., Karaarslan, C., Allred, T.
+B., Colloff, M.
+F., Karashiali, C., Sunami, N., Habib, S., Hassan, W., Brohmer, H., Dujols, O., Feldman, G., Ahmed, A., Bosch, J., Bai, H., Friedemann, M., Rojas-Berscia, L.
+M., Maturan, P.
+L.
+G., Walasek, L., Adoric, V.
+C., Carpentier, J., Joy-Gaba, J.
+A., Zabel, C., Ebersole, C.
+R., Chartier, C.
+R., Mallik, P.
+R., Urry, H.
+L., Buchanan, E.
+M., Coles, N.
+A., Primbs, M., Basnight-Brown, D., IJzerman, H., Forscher, P.
+S., & Moshontz, H., (in press).
+A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic.
+Nature Human Behaviour.
+
+### 2021
+
+- Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(2021) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students.
+Current Psychology.
+https://doi.org/10.1007/s12144-020-01287-x
+
+- van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2011) Strong public claims may not reflect researchers’ private convictions.
+Significance, 18(1), 44-45.
+
 ### 2020
+
+- Kato, A., Kunisato, Y., Katahira, K., Okimura, T., & Yamashita, Y.
+(2020) Computational Psychiatry Research Map (CPSYMAP): a New Database for Visualizing Research Papers.
+Frontiers in Psychiatry, 11, 1360.
 

### 2021-07-24 yoshihiko-kunisato.Rmd
update

@@
 ####  Yoshihiko Kunisato
-####  Associate Professor of Clinical Psychology
+####  Professor of Clinical Psychology
 ####  Department of Psychology,School of Human Sciences, SENSHU UNIVERSITY
@@
 ####  2011 - 2013 Research Associate,Faculty of Human Sciences, Waseda University
-####  2013 -2015 Lecturer (with tenure),Faculty of Human Sciences, Senshu University
-####  2015- Associate Professor, Faculty of Human Sciences, Senshu University
+####  2013 - 2015 Lecturer (with tenure),Faculty of Human Sciences, Senshu University
+####  2015 - 2021 Associate Professor, Faculty of Human Sciences, Senshu University
+####  2021 - Professor, Faculty of Human Sciences, Senshu University
 

### 2023-03-13 articles.Rmd
update

--- 2020-07-23 articles.Rmd
@@
 
+### in press
+
+- [43] Buchanan, E. M., ... Kunisato, Y., ... Primbs, M. (in press).
+The Psychological Science Accelerator's COVID-19 rapid-response dataset.
+Scientific Data.
+
+- [42] Kowal, M.,...
+Kunisato, Y., ...Zumárraga-Espinosa, M.(in press) Predictors of Enhancing Human Physical Attractiveness: Data from 93 Countries.
+Evolution and Human Behavior.[Link](https://www.sciencedirect.com/science/article/pii/S1090513822000472)
+
+### 2022
+
+- [41] Dorison, C.A., Lerner, J.S., Heller, B.H...
+Kunisato, Y.,...
+Nicholas A.
+Coles (2022).
+In COVID-19 Health Messaging, Loss Framing Increases Anxiety with Little-to-No Concomitant Benefits: Experimental Evidence from 84 Countries.
+Affective Science.
+[link](https://doi.org/10.1007/s42761-022-00128-3)
+
+- [40] Hasegawa, A., Oura, S., Yamamoto, T., Kunisato, Y., Fukui, Y.(2022) Preliminary validation of the self-report measure assessing experiences of negative independent and dependent event frequency in japanese university students.
+Journal of Rational-Emotive & Cognitive-Behavior Therapy.
+[Link](https://doi.org/10.1007/s10942-022-00469-9)
+
+- [39] Psychological Science Accelerator Self-Determination Theory Collaboration (2022).
+A global experiment on motivating social distancing during the COVID-19 pandemic.
+Proceedings of the National Academy of Sciences, 119(22), e2111091119.
+[Link](https://doi.org/10.1073/pnas.2111091119)
+
+- [38] Somatori, K.
+& Kunisato, Y.
+(2022) Metacognitive Ability and the Precision of Confidence.
+Frontiers in Human Neuroscience, section Cognitive Neuroscience [Link](https://www.frontiersin.org/articles/10.3389/fnhum.2022.706538/abstract)
+
+- [37] Hasegawa, A., Oura, S., Yamamoto, T., Kunisato, Y., Matsuda, Y., & Adachi, M.
+(2022) Causes and consequences of stress generation: Longitudinal associations of negative events, aggressive behaviors, rumination, and depressive symptoms.
+Current Psychology.[link](https://doi.org/10.1007/s12144-022-02859-9)
+
+### 2021
+
+- [36] Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y.
+(2021).
+Depression, rumination, and impulsive action: A latent variable approach to behavioral impulsivity.
+The Journal of Psychology, 155(8), 717-737.
+[link](https://doi.org/10.1080/00223980.2021.1956871)
+
+- [35] Kashihara, J., Takebayashi, Y., Kunisato, Y., & Ito, M.
+(2021) Classifying patients with depressive and anxiety disorders according to symptom network structures: A Gaussian graphical mixture model-based clustering.
+PLoS ONE 16(9): e0256902.
+[Link](https://doi.org/10.1371/journal.pone.0256902)
+
+- [34] Wang K., Goldenberg A., Dorison, C.A., Miller, J.K., Uusberg, A., Lerner, J.S., Gross, J.J., Agesin, B.B., Bernardo, M., Campos, O., Eudave, L., Grzech, K., Ozery, D.H., Jackson, E.A., Luis Garcia, E.O., Drexler, S.M., Jurković, A.P., Rana, K., Wilson, J.P., ...
+Kunisato, Y.,...Moshontz, H.
+(in press) A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic.
+Nature Human Behavior, 5, 1089–1110.[Link](https://doi.org/10.1038/s41562-021-01173-x)
+
+- [33] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(2021) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students.
+Current Psychology.
+[Link](https://doi.org/10.1007/s12144-020-01287-x)
+
+- [32] van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2011) Strong public claims may not reflect researchers' private convictions.
+Significance, 18(1), 44-45.[Pre Print](https://psyarxiv.com/pc4ad/)
+
 ### 2020
 
-- Katahira, K., Kunisato, Y., Okimura, T., & Yamashita, Y.
+- [31] Kato, A., Kunisato, Y., Katahira, K., Okimura, T., & Yamashita, Y.
+(2020) Computational Psychiatry Research Map (CPSYMAP): a New Database for Visualizing Research Papers.
+Frontiers in Psychiatry, 11, 1360.[Link](https://www.frontiersin.org/articles/10.3389/fpsyt.2020.578706/full)
+
+- [30] Katahira, K., Kunisato, Y., Okimura, T., & Yamashita, Y.
 (2020) Retrospective surprise: A computational component for active inference.
@@
 
-- Katahira, K., Kunisato, Y., Yamashita, Y., & Suzuki, S.
+- [29] Katahira, K., Kunisato, Y., Yamashita, Y., & Suzuki, S.
 (2020) Commentary: "A robust data-driven approach identifies four personality types across four large data sets".
@@
 
-- Nishiguchi, Y., Sakamoto, J., Kunisato, Y., & Takano, K.
+- [28] Nishiguchi, Y., Sakamoto, J., Kunisato, Y., & Takano, K.
 (2019) Linear Ballistic Accumulator Modeling of Attentional Bias Modification Revealed Disturbed Evidence Accumulation of Negative Information by Explicit Instruction.
@@
 
-- Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K.
+- [27] Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K.
 (2019).
@@
 
-- Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y.
+- [26] Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y.
 (2019).
@@
 
-- Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
+- [25] Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
 (2018).
@@
 
-- Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
+- [24] Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y.
 (2018).
@@
 
-- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T.
+- [23] Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T.
 A., & Yamawaki.
@@
 
-- Moriguchi, Y., Noda, T., Nakayashiki, K., Takata, Y., Setoyama, S., Kawasaki, S., Kunisato, Y., Mishima, K., Nakagome, K., Hanakawa, T.
+- [22] Moriguchi, Y., Noda, T., Nakayashiki, K., Takata, Y., Setoyama, S., Kawasaki, S., Kunisato, Y., Mishima, K., Nakagome, K., Hanakawa, T.
 (2017).
@@
 
-- Yoshimura, S., Okamoto, Y., Matsunaga, M., Onoda, K., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S.
+- [21] Yoshimura, S., Okamoto, Y., Matsunaga, M., Onoda, K., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S.
 (2017).
@@
 
-- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, A.
+- [20] Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, A.
 T., & Yamawaki.
@@
 
-- Hasegawa, A., Nishimura, H., Matsuda, Y., Kunisato, Y., Morimoto, H., & Adachi, M.
+- [19] Hasegawa, A., Nishimura, H., Matsuda, Y., Kunisato, Y., Morimoto, H., & Adachi, M.
 (2016).
@@
 
-- Tsukue, R., Okamoto, Y., Yoshino, A., Kunisato, Y., Takagaki, K., Takebayashi, Y., Tanaka, K., Konuma, K., Tsukue, I., & Yamawaki, S.
+- [18] Tsukue, R., Okamoto, Y., Yoshino, A., Kunisato, Y., Takagaki, K., Takebayashi, Y., Tanaka, K., Konuma, K., Tsukue, I., & Yamawaki, S.
 (2015) Do Individuals with Alcohol Dependence Show Higher Unfairness Sensitivity?
@@
 
-- Nishiyama,Y., Okamoto, Y., Kunisato, Y., Okada, G., Yoshimura, S., Kanai, Y., Yamamura, T., Yoshino, A., Jinnin, R., Takagaki, K., Onoda, K., & Yamawaki, S.
+- [17] Nishiyama,Y., Okamoto, Y., Kunisato, Y., Okada, G., Yoshimura, S., Kanai, Y., Yamamura, T., Yoshino, A., Jinnin, R., Takagaki, K., Onoda, K., & Yamawaki, S.
 (2015) fMRI Study of Social Anxiety during Social Ostracism with and without Emotional Support.
@@
 
-- Machino, A., Kunisato, Y., Matsumoto, T., Yoshimura, S., Ueda, K., Yamawaki, Y., Okada, G., Okamoto, Y., & Yamawaki, S (2014) Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, Journal of Affective Disorders, 168, 229-235.
+- [16] Machino, A., Kunisato, Y., Matsumoto, T., Yoshimura, S., Ueda, K., Yamawaki, Y., Okada, G., Okamoto, Y., & Yamawaki, S (2014) Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, Journal of Affective Disorders, 168, 229-235.
 [Link](https://www.sciencedirect.com/science/article/abs/pii/S0165032714003917?via%3Dihub)
 
-- Yoshino, A., Okamoto, Y., Kunisato, Y., Yoshimura, Y., Jinnin, R., Hayashi, Y., Kobayakawa, M., Doi, M., Oshita, K., Nakamura, R., Tanaka, K., Yamashita, H., Kawamoto, M., & Yamawaki, S.
+- [15] Yoshino, A., Okamoto, Y., Kunisato, Y., Yoshimura, Y., Jinnin, R., Hayashi, Y., Kobayakawa, M., Doi, M., Oshita, K., Nakamura, R., Tanaka, K., Yamashita, H., Kawamoto, M., & Yamawaki, S.
 (2014).
@@
 
-- Toki, S., Okamoto, Y., Onoda, K., Matsumoto, T., Yoshimura, S., Kunisato, Y., Okada, G., Shishida, K., Kobayakawa, M., Fukumoto, T., Machino, A., Inagaki, M., Yamawaki, S.
+- [14] Toki, S., Okamoto, Y., Onoda, K., Matsumoto, T., Yoshimura, S., Kunisato, Y., Okada, G., Shishida, K., Kobayakawa, M., Fukumoto, T., Machino, A., Inagaki, M., Yamawaki, S.
 (2014).
@@
 
-- Yoshimura, S., Okamoto, Y., Onoda, K., Matsunaga, M., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S.
+- [13] Yoshimura, S., Okamoto, Y., Onoda, K., Matsunaga, M., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S.
 (2013).
@@
 
-- Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., Kanai, Y., Ishikawa, S., & Sakano, Y.
+- [12] Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., Kanai, Y., Ishikawa, S., & Sakano, Y.
 (2013).
@@
 
-- Koseki, S., Noda., T., Yokoyama, S., Kunisato, Y., Ito, D., Suyama, H., Matsuda, T., Sugimura, Y., Ishihara, N., Shimizu, Y., Nakazawa, K., Yoshida, S., Arima, K., Suzuki,S.
+- [11] Koseki, S., Noda., T., Yokoyama, S., Kunisato, Y., Ito, D., Suyama, H., Matsuda, T., Sugimura, Y., Ishihara, N., Shimizu, Y., Nakazawa, K., Yoshida, S., Arima, K., Suzuki,S.
 (2013).
@@
 
-- Kinoshita, A., Okamoto, Y., Okada, G., Demoto, Y., Kunisato, Y., Yoshimura, S., Onoda,K., Kamachi, M., Yamawaki, S.
+- [10] Kinoshita, A., Okamoto, Y., Okada, G., Demoto, Y., Kunisato, Y., Yoshimura, S., Onoda,K., Kamachi, M., Yamawaki, S.
 (2012) Sex differences in neural activation to ambiguous facial expression in happy and sad context, Perceptual and Motor Skills, 115(2), 349-359.
@@
 
-- Kunisato, Y., Okamoto, Y., Ueda, K., Onoda, K., Okada, G., Yoshimura, S., Suzuki, S., Samejima, K., Yamawaki, S.
+- [9] Kunisato, Y., Okamoto, Y., Ueda, K., Onoda, K., Okada, G., Yoshimura, S., Suzuki, S., Samejima, K., Yamawaki, S.
 (2012) Effects of depression on reward based decision making and variability of action in probabilistic learning, Journal of Behavior Therapy and Experimental Psychiatry, 43, 1088-1094.
@@
 
-- Yoshino, A., Okamoto, Y., Onoda, K., Shishida, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G., Toki, S., Yamashita, H., Yamawaki, S.
+- [8] Yoshino, A., Okamoto, Y., Onoda, K., Shishida, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G., Toki, S., Yamashita, H., Yamawaki, S.
 (2012) Sadness enhances the experience of pain and affects pain-evoked cortical activities: An MEG study, The Journal of Pain,13, 628-635.
@@
 
-- Demoto, Y., Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Onoda, K., Munakata, A., Nomura, M., Tanaka, S.
+- [7] Demoto, Y., Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Onoda, K., Munakata, A., Nomura, M., Tanaka, S.
 C., Schweighofer, N., Doya, K., Yamawaki, S.
@@
 
-- Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Nishiyama, Y., Yoshimura, S., Onoda, K., Toki, S., Yamashita, H., & Yamawaki, S.
+- [6] Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Nishiyama, Y., Yoshimura, S., Onoda, K., Toki, S., Yamashita, H., & Yamawaki, S.
 (2011) The effect of negative and positive emotionality on associative memory: An fMRI study, PLoS ONE, 6(9),e24862.
@@
 
-- Onoda, K., Okamoto, Y., Kunisato, Y., Aoyama, S., Shishida, K., Okada, G., Tanaka, SC., Schweighofer, N., Yamaguchi, S., Doya, K., & Yamawaki, S.
+- [5] Onoda, K., Okamoto, Y., Kunisato, Y., Aoyama, S., Shishida, K., Okada, G., Tanaka, SC., Schweighofer, N., Yamaguchi, S., Doya, K., & Yamawaki, S.
 (2011) Inter-individual discount factor differences in reward prediction are topographically associated with caudate activation, Experimental Brain Research, 212(4), 593-601.
@@
 
-- Kunisato, Y., Okamoto, Y., Okada, G., Aoyama, S., Nishiyama, Y., Onoda, K., Yamawaki, S.
+- [4] Kunisato, Y., Okamoto, Y., Okada, G., Aoyama, S., Nishiyama, Y., Onoda, K., Yamawaki, S.
 (2011)Personality traits and the amplitude of spontaneous low-frequency oscillations during resting state, Neuroscience Letters, 492(2), 109-113.
@@
 
-- Kunisato,Y., Okamoto, Y., Okada, G., Aoyama, S., Demoto, Y., Munakata, A., Nomura, M., Onoda, K., Yamawaki, S.
+- [3] Kunisato,Y., Okamoto, Y., Okada, G., Aoyama, S., Demoto, Y., Munakata, A., Nomura, M., Onoda, K., Yamawaki, S.
 (2011) Modulation of default - mode network activity by acute tryptophan depletion is associated with mood change：A resting state functional magnetic resonance imaging study.
@@
 
-- Matsunaga, M., Okamoto, Y., Suzuki, S., Kinoshita, A., Yoshimura, S., Yoshino, A., Kunisato, Y.
+- [2] Matsunaga, M., Okamoto, Y., Suzuki, S., Kinoshita, A., Yoshimura, S., Yoshino, A., Kunisato, Y.
 & Yamawaki, S.
@@
 
-- Yoshino, A., Okamoto, Y., Onoda, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G, & Shigeto, Y.
+- [1] Yoshino, A., Okamoto, Y., Onoda, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G, & Shigeto, Y.
 (2010).

### 2023-03-13 team.Rmd
update

@@
 
-- Keisuke Inoue
-- Satoshi Yamazaki
+- Yukiko Saito
+- Mayu Obata
+- Ayuri Kai
 
@@
 
-- Yukiko Saito
-- Jihee Woo
-- Ryota Tanaka
-- Daichi Igarashi
-- Naoki Sawamura
-- Shu Ensei
 - Koji Komine
+- Kaichu Kyo
+- Yura Muraguchi
+- Mayu Okano
+- Masataka Sumida
+- Kana Warashina
+- Amane Suzuki
+- Rryuji Yamagishi
+- Takumi Omizu
+- Syouto Hirai
+- Kurumi Tajima
+- Hiyori Kato
